Brownian Dynein Model

### 2016-06-13 latex/paper.tex
fix a few bugs while meeting together

\newcommand{\mn}{\scalebox{0.7}[1.0]{-}}

@@

\begin{align}
  \frac{dX_{t}}{dL_n} &= \cos\theta_n\\
  \frac{dY_{t}}{dL_n} &= \sin\theta_n\\
  \frac{dX_{t}}{dL_f} &= 0\\
  \frac{dY_{t}}{dL_f} &= 0\\
\end{align}

@@

\begin{align}
  \dot{X}_{nm} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{ns}(X_{bm} - X_{bb})
  + \lambda_{nt}(X_{t } - X_{bm}) \Big) + R_{xml}
  &=& \frac{X_{nm}}{Ln}\dot{L}_n + \frac{X_{nm}}{Lf}\dot{L}_f\\
  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{nt}(X_{t } - X_{bm})
  + \lambda_{ft}(X_{fm} - X_{t }) \Big) + R_{xt }
  &=& \frac{X_{t}}{Ln}\dot{L}_n + \frac{X_{t}}{Lf}\dot{L}_f\\
  \dot{X}_{fm} &= \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{ft}(X_{fm} - X_{t })
  + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr}
  &=& \frac{X_{fm}}{Ln}\dot{L}_n + \frac{X_{fm}}{Lf}\dot{L}_f
\end{align}

\begin{align}
  \dot{Y}_{nm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{ns}(Y_{bm} - Y_{bb})
  + \lambda_{nt}(Y_{t } - Y_{bm}) \Big) + R_{yml}
  &= \frac{Y_{nm}}{Ln}\dot{L}_n + \frac{Y_{nm}}{Lf}\dot{L}_f\\
  \dot{Y}_{t}  &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{nt}(Y_{t } - Y_{bm})
  + \lambda_{ft}(Y_{fm} - Y_{t }) \Big) + R_{yt }
  &= \frac{Y_{t}}{Ln}\dot{L}_n + \frac{Y_{t}}{Lf}\dot{L}_f\\
  \dot{Y}_{fm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{ft}(Y_{fm} - Y_{t })
  + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr}
  &= \frac{Y_{fm}}{Ln}\dot{L}_n + \frac{Y_{fm}}{Lf}\dot{L}_f
\end{align}

>>>>

@@

\begin{align}
  \frac{dX_{t}}{dL_n} &= \cos\theta_n + L_n\frac{\partial \cos\theta_n}{\partial L_n} &= \frac{L_n}{L}\\
  \frac{dY_{t}}{dL_n} &= \sin\theta_n + L_n\frac{\partial \sin\theta_n}{\partial L_n}\\
  \frac{dX_{t}}{dL_f} &= L_n\frac{\partial \cos\theta_n}{\partial L_f} &= -\frac{L_f}{L}\\
  \frac{dY_{t}}{dL_f} &= L_n\frac{\partial \sin\theta_n}{\partial L_f}\\
\end{align}

@@

\begin{align}
  \dot{X}_{nm} &= \frac{1}{\gamma} \Big(F_{xml} - \lambda_{ns}(X_{bm} - X_{bb})
  + \lambda_{nt}(X_{t } - X_{bm}) \Big) + R_{xml}
  &=& \frac{\partial X_{nm}}{\partial L_n}\dot{L}_n + \frac{\partial X_{nm}}{\partial L_f}\dot{L}_f\\
  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } - \lambda_{nt}(X_{t } - X_{bm})
  + \lambda_{ft}(X_{fm} - X_{t }) \Big) + R_{xt }
  &=& \frac{\partial X_{t}}{\partial L_n}\dot{L}_n + \frac{\partial X_{t}}{\partial L_f}\dot{L}_f\\
  \dot{X}_{fm} &= \frac{1}{\gamma} \Big(F_{xmr} - \lambda_{ft}(X_{fm} - X_{t })
  + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr}
  &=& \frac{\partial X_{fm}}{\partial L_n}\dot{L}_n + \frac{\partial X_{fm}}{\partial L_f}\dot{L}_f
\end{align}

\begin{align}
  \dot{Y}_{nm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yml} - \lambda_{ns}(Y_{bm} - Y_{bb})
  + \lambda_{nt}(Y_{t } - Y_{bm}) \Big) + R_{yml}
  &= \frac{\partial Y_{nm}}{\partial L_n}\dot{L}_n + \frac{\partial Y_{nm}}{\partial L_f}\dot{L}_f\\
  \dot{Y}_{t}  &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{yt } - \lambda_{nt}(Y_{t } - Y_{bm})
  + \lambda_{ft}(Y_{fm} - Y_{t }) \Big) + R_{yt }
  &= \frac{\partial Y_{t}}{\partial L_n}\dot{L}_n + \frac{\partial Y_{t}}{\partial L_f}\dot{L}_f\\
  \dot{Y}_{fm} &= \hspace{1cm} \frac{1}{\gamma} \Big(F_{ymr} - \lambda_{ft}(Y_{fm} - Y_{t })
  + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr}
  &= \frac{\partial Y_{fm}}{\partial L_n}\dot{L}_n + \frac{\partial Y_{fm}}{\partial L_f}\dot{L}_f
\end{align}
